\documentclass[11pt]{article}
\usepackage{hyperref}

\title{My \LaTeX\ Document}
\author{Tom Harper}
% \date{December 16th, 2023}
\date{\today}

\begin{document}
\tableofcontents %note it takes two compiles for this to render

\maketitle

This will produce \textit{italicized} text.

This will produce \textbf{bold face} text.

This will produce \textsc{small caps} text.

This will proudce \texttt{typewriter font} text.

Please visit Michelle Krummel's website at \url{http://michellekrummel.com}.

Please visit Michelle Krummel's website at \href{http://michellekrummel.com}{My Wesbsite}.

\vspace{1cm}

Please excuse my dear aunt Sally

Please excuse my \begin{large}dear aunt Sally\end{large}.

Please excuse my \begin{Large}dear aunt Sally\end{Large}.

Please excuse my \begin{huge}dear aunt Sally\end{huge}.

Please excuse my \begin{Huge}dear aunt Sally\end{Huge}.

Please excuse my \begin{normalsize}dear aunt Sally\end{normalsize}.

Please excuse my \begin{small}dear aunt Sally\end{small}.

Please excuse my \begin{scriptsize}dear aunt Sally\end{scriptsize}.

Please excuse my \begin{tiny}dear aunt Sally\end{tiny}.

\vspace{1cm}

\begin{center}This line is centered.\end{center}
\begin{flushleft}This line is left justified.\end{flushleft}
\begin{flushright}This line is right justified.\end{flushright}

\tiny

This line is centered.

This line is left justified.

This line is right justified.

% can use section*{} (notice the star) to remove numbering
\section{Linear Functions}
    \subsection{Slope-Intercept Form}
        \subsubsection{Example 1:}
        \subsubsection{Example 2:}
    \subsection{Standard Form}
    \subsection{Point-Slope Form}
\section{Quadratic Functions}
    \subsection{Vertex Form}
    \subsection{Standard Form}
    \subsection{Factored Form}

\end{document}
